---
title: "SEtupScript"
author: "Tania Raugewitz, MBA, PSM"
date: "`r Sys.Date()`"
output: html_document
---
Git Commands
Order is important! Your general git workflow should be as follows:

a: Fresh repo, does not yet exist on your local machine (only do this ONCE per project/machine)

⦁	git clone [copied HTTPS repo URL] : This will create a folder in whatever your current working directory is (see with pwd) with the same name as your GitHub repository and a copy of all the files in that repository. 
⦁	DO NOT manually create a folder with the repo name, git clone will do that for you.

b: Existing repo, fresh session/work day (after you've git cloned)
⦁	git pull : This is to make sure any changes up on GitHub are copied to your local repo 
1.		(extra important if you are collaborating with others)

⦁	git add [filename] to add/stage a specific file or git add . to add all untracked files 
1.	(remember to SAVE your files first, otherwise git will not be tracking it).

⦁	git commit -m "unique commit message" : commit all added/staged files, with a short but informative message describing those file changes
Note: 
1.	you can add/commit multiple times and multiple files before pushing everything. 
2.	But just don’t forget to push at the end!

⦁	git push : send everything that you’ve committed to GitHub

Throughout the above workflow use git status to check:
1.	the status of your files, 
2.	which are untracked, 
3.	which are staged and ready to commit, 
4.	is everything ready to push to GitHub?

You can also use this git commands cheatsheet, which has even more commands you can use.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

Make sure our setup.r is setup correctly


```{r}
packageLoad <-
  function(x) {
    for (i in 1:length(x)) {
      if (!x[i] %in% installed.packages()) {
        install.packages(x[i])
      }
      library(x[i], character.only = TRUE)
    }
  }

# create a string of package names
packages <- c('tidyverse',
              'palmerpenguins',
              'lterdatasampler')

packageLoad(packages)
```


source("setup.R")

git status

git clone pull then add, commit, push.
Load data
```{r}
data("knz_bison")
```


#```{r}
data <- read_csv(data/kenya...)
```

